NeuroElectro: A Window to the World's Neuron Electrophysiology Data

### 2014-03-17 neuroelectro_frontiers/main.tex
updated main.tex and updated figures

\begin{figure*}[htbp!]
\centering
\includegraphics[scale = 1]{figures/metadata_assignment_accuracy.jpg}
\caption{\textit{Accuracy of metadata assignment using automated methods alone.} }
\label{metadata_robot_accuracy_robot}
\end{figure*}

@@

Future developments in machine extraction of data from the scientific literature will be of great benefit.  
These should include better semantic understanding of context, ranging from relatively unambiguous notations such as units, to syntax-parsing that relates objects of study to their reported properties in free-form prose.  
Much progress has been made by computer scientists in some of these areas, and more future engagement with their research should enable vastly more data to be extracted from the literature.  
In the mean time, experimentalists who would like their data to be easily curated should strongly consider using data tables in future publications.

>>>>

\begin{figure*}[htbp!]
\centering
\includegraphics[scale = 1]{figures/metadata_assignment_accuracy_v2.jpg}
\caption{\textit{Accuracy of metadata assignment using automated methods alone.} }
\label{metadata_robot_accuracy_robot}
\end{figure*}

@@

Future developments in machine extraction of data from the scientific literature will be of great benefit.  
These should include better semantic understanding of context, ranging from relatively unambiguous notations such as units, to syntax-parsing that relates objects of study to their reported properties in free-form prose.  
Much progress has been made by computer scientists in some of these areas, and more future engagement with their research should enable vastly more data to be extracted from the literature.

To facilitate further data integration efforts, we advocate small shifts in how investigators analyze and report neurophysiological data.  
Specifically, we recommend the usage of common standards and definitions for basic physiological measurements\citep{toledo-rodriguez_correlation_2004} and neuron types\citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.  
We also ask that physiologists report more basic physiological information within articles and, if possible, publish such data using machine-readable formats like data tables.  
Similarly, relevant experimental details should be clearly stated within the methods section (e.g., liquid junction potential correction).  
These recommendations could be made informally by journals (in particular, requested by reviewers during manuscript review) as well as by funding agencies.
